Evaluating a simplified forecast model in comparison to the ECDC forecasting hub ensemble

### 2022-06-07 docs/paper/paper.Rmd
more plot tuning

```{r make-rwis-plots}
plot_rwis_horizon <- relative_wis |>
  copy() |>
  DT(, horizon := fct_rev(as.factor(horizon))) |>
  plot_relative_wis(
    y = horizon, fill = horizon,
    point_color = horizon
  ) +
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2") +
  labs(y = "Forecast horizon (weeks)") +
  guides(fill = guide_none(), point_color = guide_none())

@@

plot_rwis_by_month <- relative_wis |>
  DT(horizon == 1 | horizon == 4) |>
  DT(, target_month := month(target_end_date, label = TRUE)) |>
  DT(, target_month := fct_rev(target_month)) |>
  plot_relative_wis(
    y = target_month, fill = as.factor(horizon), alpha = 0.3,
    jittered_points = TRUE, quantiles = NULL
  ) +
  scale_fill_brewer(palette = "Dark2") +
  labs(y = "Target forecast month", fill = "Forecast horizon (weeks)")
```

>>>>

```{r make-rwis-plots}
plot_rwis_horizon <- relative_wis |>
  copy() |>
  DT(, horizon := fct_rev(as.factor(horizon))) |>
  plot_relative_wis(
    y = horizon, fill = horizon
  ) +
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2") +
  labs(y = "Forecast horizon (weeks)") +
  guides(fill = guide_none(), point_color = guide_none(), point = guide_none())

@@

plot_rwis_by_month <- relative_wis |>
  DT(horizon == 1 | horizon == 4) |>
  DT(, target_month := month(target_end_date, label = TRUE)) |>
  DT(, target_month := fct_rev(target_month)) |>
  plot_relative_wis(
    y = target_month, fill = as.factor(horizon), alpha = 0.3,
    jittered_points = TRUE, quantiles = NULL
  ) +
  scale_fill_brewer(palette = "Dark2") +
  labs(y = "Target forecast month", fill = "Forecast horizon (weeks)") +
  guides(fill = guide_none())
```
